### 2022-04-02 README.Rmd
Added all raw data and began a data preparation .rmd.

Currently, the following raw data from Madrid is contained here:

-  "parque_vehiculos_2021"  includes vehicle fleet characteristics of Madrid City. Of interest: the district and the environmental label associated to each vehicle.

>>>>

Currently, the data contained in this repository is from the [Madrid City Council](https://datos.madrid.es/portal/site/egob/menuitem.c05c1f754a33a9fbe4b2e4b284f1a5a0/?vgnextoid=128b5dda42c84410VgnVCM2000000c205a0aRCRD&vgnextchannel=374512b9ace9f310VgnVCM100000171f5a0aRCRD&vgnextfmt=default) and the [Community of Madrid](https://datos.comunidad.madrid/catalogo/dataset/resultados-edm2018) databases retrieved March 31st 2022. It includes the following:

-  "parque_vehiculos_2021", "2020", and "2019",  includes vehicle fleet characteristics of Madrid City. Of interest: the district and the environmental label associated to each vehicle.
